Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-11-20 summary.tex
SDASDASDASDSADAS

@@

\section{Discussion}

\vspace{0.5em}

\subsection{Essential Subroutines}
\label{sec:esubroutine}

@@

\subsection{Extensions}

@@

\vspace{0.5em}
\noindent\textbf{Classification acceleration}~~~~If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly. Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.

@@

\section{Experiments}

>>>>

\subsection{Classification Acceleration}
\label{sec:acc}
If the CSG tree is large with hundreds of primitive nodes, computing $\lambda_f(\bm{s}_i)$ from $\boldsymbol{\Lambda}(\bm{s}_i)$ for every face $\bm{s}_i$ can be costly. Thanks to the indicator space coherence, we can save the computation time by caching the evaluation result $f(\boldsymbol{\Lambda}(\bm{s}_i))$ during flood-filling.

\subsection{Deferred Tessellation}
We find for a CSG with many meshes, a large percentage of intersections are not necessary to produce the final result (Fig. \ref{}). Thus tessellating according to every detected intersections is not necessary. Using the accelerating strategy in \S\ref{sec:acc}, we can use the intersections information of faces to give an early prediction of whether the face have to be tessellated.

@@

\fi
\section{Experiments}

\begin{table*}[ht]
\caption{Computation Time Statistics (Seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{13}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
\multirow{2}{*}{No.} & \multirow{2}{*}{Figure} & \multicolumn{3}{c|}{Face Num.$^\nabla$} & \multirow{2}{*}{\tabincell{c}{Primitive\\Count}} & \multirow{2}{*}{\tabincell{c}{CGAL}} & \multirow{2}{*}{\tabincell{c}{Maya}} & \multirow{2}{*}{\tabincell{c}{Cork/Carve}} & \multirow{2}{*}{\tabincell{c}{QuickCSG}}& \multicolumn{4}{c}{Our Approach}\\
\cline{3-5} \cline{11-14}
 & & Total & Min & Max &&&&&& Total$^\circ$ & Step 1 & Step 2 & Step 3\\
\hline \hline
1 & \ref{fig:models}(a) & 37.6K & 180 & 1.6K & 201 & 1350 & 49.9 & - & 15.9 & \textbf{3.13}  & 0.328 & 1.69 & 0.922 \\
2 & \ref{fig:models}(a) & 146K & 180 & 1.6K & 801  & TLE & 1400 & TLE & Fail* & \textbf{12.8}  & 1.36 & 6.41 & 4.00 \\
3 & \ref{fig:models}(b) & 377K & 2.56K & 346K & 7 & TLE & 224.5 & 45.7 & 11.7 & \textbf{1.44} & 0.438 & 0.062 & 0.563 \\
4 & \ref{fig:models}(c) & 79.2K & 12 & 38.2K & 4  & 97.6 & Fail & 3.58 & 1.69 & \textbf{0.563}  & 0.187 & 0.141 & 0.172 \\
5 & \ref{fig:models}(d) & 36K & 800 & 2.4K & 29 & 34.1 & 7.03 & 18.7 & 4.05 & \textbf{0.313} & 0.094 & 0.094 & 0.081 \\
6 & \ref{fig:models}(e) & 597K & 96.9K & 500K & 2 & TLE & 38.3 & 26.4 & 5.63 & \textbf{2.13} & 0.563 & 0.031 & 0.984 \\
7 & \ref{fig:models}(f) & 170K & 69.7K & 100K & 2  & 218 & 7.45 & 13.8 & 2.39 & \textbf{0.891} & 0.328 & 0.125 & 0.266 \\
8 & \ref{fig:models}(g) & 362K & 6.91K & 276K & 22 & TLE & 344 & 256 & 19.2 & \textbf{1.80} & 0.766 & 0.172 & 0.593 \\
9 & \ref{fig:budda} & 2.16M & 1.08M & 1.08M & 2 & Fail & Fail & MLE$^\bullet$ & Fail & \textbf{11.3} & 5.55 & 1.36 & 3.01 \\
\hline
\end{tabular}
\begin{flushleft}
$^{\nabla}$~~\emph{Min} (\emph{Max}) means the minimum (maximum) number of faces of a single primitive.

$^{\circ}$~~The total computation time of our method includes the construction of half-edge structure and the three steps in Section \ref{sec:overview}.

\end{flushleft}
\end{table*}

We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM. To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity. Extreme degenerate cases such as self-union are also tested.

We compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.

\vspace{0.5em}
\noindent\textbf{Coplanar and self-union}~~~~
Our method is unconditionally robust for regular set meshes. Even extreme degenerate cases will not cause invalid output. To prove that, we tested the self-union of several models and some CSG with coplanar faces. We find that our method always produces visually correct results. QuickCSG and Cork failed to produce the result in most of these cases, because they cannot deal with coplanar faces. Even after perturbation, the result meshes are still full with deficiencies (holes, boundary edges, etc.). For the bunny model, we found our result face count was slightly deviation from the original mesh. This is because the original mesh contains self-intersection in the bunny chest (the green faces).

\vspace{0.5em}
\noindent\textbf{Binary boolean operations}~~~~
The most common situation of CSG evaluation is to perform boolean operations one by one, since many designers are used to change the model progressly. While our method can evaluate multiple boolean operations once for all, we compared the performance of binary boolean operations to prove the efficiency. Table \ref{tab:performance} shows the evaluation time of different methods. We can clearly see our method is very fast that is only slightly slower than the fastest non-robust QuickCSG. Other robust methods such as Maya and CGAL are much slower because both of them use the arbitrary precision arithmetic. It should be noted that in some cases (), most time is spent on octree construction. It means other stages which involve plane-based geometry take only a small percentage of time, proving the efficiency of our plane-based geometry.

\vspace{0.5em}
\noindent\textbf{CSGs with many primitives}~~~~
To identify the ability of evaluating large CSG, we also test some CSG with tens or hundreds of meshes. Maya and CGAL cannot perform multiple boolean operations, so we can only give the comparison of incremental boolean evaluation. We

\section{Essential Subroutines}
\label{sec:esubroutine}

@@

\section{Extensions}

@@

@@
